Comparing Optimization Algorithms in the Fitting of Linear Mixed Models: Evaluating Speed and Accuracy using \pkg{lme4} in R and \pkg{lmm} in Julia

### 2015-08-27 inst/doc/Paper.Rnw
Used correct chunk options and fixed table float issue

\begin{document}
\SweaveOpts{concordance=FALSE}
%% include your article here, just as usual
%% Note that you should use the \pkg{}, \proglang{} and \code{} commands.

@@

\begin{table}[htbp]
\centering
\begin{tabular}{rllrrrrrr}
  \hline
 & opt & dsname & n & p & np & excess & time & reltime \\ 
  \hline
1 & LD\_CCSAQ & Alfalfa &  72 &  12 &   1 & 0.00 & 0.00 & 1.13 \\ 
  2 & LD\_CCSAQ & AvgDailyGain &  32 &   8 &   1 & 0.00 & 0.00 & 0.82 \\ 
  3 & LD\_CCSAQ & AvgDailyGain &  32 &   5 &   1 & 0.00 & 0.00 & 0.93 \\ 
  4 & LD\_CCSAQ & BIB &  24 &   8 &   1 & 0.00 & 0.00 & 0.79 \\ 
  5 & LD\_CCSAQ & Bond &  21 &   3 &   1 & 0.00 & 0.00 & 1.03 \\ 
  6 & LD\_CCSAQ & bs10 & 1104 &   4 &  20 & 0.00 & 1.10 & 4.44 \\ 
  7 & LD\_CCSAQ & bs10 & 1104 &   4 &   8 & 39.99 & 0.04 & 0.56 \\ 
  8 & LD\_CCSAQ & cake & 270 &  18 &   1 & 0.00 & 0.00 & 1.37 \\ 
  9 & LD\_CCSAQ & Cultivation &  24 &   6 &   1 & 0.00 & 0.00 & 0.99 \\ 
  10 & LD\_CCSAQ & Demand &  77 &   5 &   2 & 3.22 & 0.01 & 0.81 \\ 
  11 & LD\_CCSAQ & dialectNL & 225866 &   4 &   6 & 0.00 & 6.99 & 3.99 \\ 
  12 & LD\_CCSAQ & Dyestuff2 &  30 &   1 &   1 & 0.00 & 0.00 & 0.68 \\ 
  13 & LD\_CCSAQ & Dyestuff &  30 &   1 &   1 & 0.00 & 0.00 & 1.02 \\ 
  14 & LD\_CCSAQ & ergoStool &  36 &   4 &   1 & 0.00 & 0.00 & 1.10 \\ 
  15 & LD\_CCSAQ & Exam & 4059 &   5 &   1 & 0.00 & 0.01 & 1.19 \\ 
  16 & LD\_CCSAQ & Exam & 4059 &   6 &   1 & 0.00 & 0.01 & 1.32 \\ 
  17 & LD\_CCSAQ & Gasoline &  32 &   2 &   1 & 0.00 & 0.00 & 0.82 \\ 
  18 & LD\_CCSAQ & gb12 & 512 &   8 &  20 & 0.00 & 3.52 & 17.48 \\ 
  19 & LD\_CCSAQ & gb12 & 512 &   8 &   8 & 103.18 & 0.02 & 0.56 \\ 
  20 & LD\_CCSAQ & HR & 120 &   7 &   3 & 0.00 & 0.01 & 1.22 \\ 
  21 & LD\_CCSAQ & Hsb82 & 7185 &   5 &   1 & 192.73 & 0.01 & 0.49 \\ 
  22 & LD\_CCSAQ & IncBlk &  24 &   8 &   1 & 0.56 & 0.00 & 0.66 \\ 
  23 & LD\_CCSAQ & kb07 & 1790 &   8 &  72 & 8.21 & 17.47 & 4.12 \\ 
  24 & LD\_CCSAQ & Mississippi &  37 &   3 &   1 & 0.93 & 0.00 & 0.67 \\ 
  25 & LD\_CCSAQ & mm0 & 69588 &   4 &   6 & 0.00 & 4.83 & 4.40 \\ 
  26 & LD\_CCSAQ & Oxboys & 234 &   2 &   3 & 136.79 & 0.02 & 0.71 \\ 
  27 & LD\_CCSAQ & PBIB &  60 &  15 &   1 & 0.00 & 0.00 & 1.00 \\ 
  28 & LD\_CCSAQ & Penicillin & 144 &   1 &   2 & 0.00 & 0.01 & 4.94 \\ 
  29 & LD\_CCSAQ & Semiconductor &  48 &  16 &   1 & 0.00 & 0.00 & 1.05 \\ 
  30 & LD\_CCSAQ & SIMS & 3691 &   2 &   3 & 3.61 & 0.13 & 0.99 \\ 
  31 & LD\_CCSAQ & sleepstudy & 180 &   2 &   3 & 0.00 & 0.01 & 1.75 \\ 
  32 & LD\_CCSAQ & sleepstudy & 180 &   2 &   2 & 0.00 & 0.00 & 1.13 \\ 
  33 & LD\_CCSAQ & TeachingII &  96 &  12 &   1 & 0.00 & 0.00 & 0.93 \\ 
  34 & LD\_CCSAQ & Weights & 399 &   6 &   3 & 99.13 & 0.02 & 0.51 \\ 
  35 & LD\_CCSAQ & WWheat &  60 &   2 &   3 & 18.20 & 0.01 & 0.68 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

\begin{document}
\SweaveOpts{concordance=FALSE}

<<>>=
load("~/Desktop/Summer_Sweave/Timings/data/res.rda")
@

%% include your article here, just as usual
%% Note that you should use the \pkg{}, \proglang{} and \code{} commands.

@@

<<echo=FALSE>>=
library(xtable)
@

\begin
{center}
<<results=tex,echo=FALSE>>=
print(xtable(subset(res, opt=="LD_CCSAQ")[1:8]), table.placement="!htp")
@
\end {center}
